Analyzing the impact of social attributes on commit integration success

### 2017-02-20 Paper/MSRChallenge2017.tex
CLG edits todos through end

\textbf{Technical Factors:} We collected these factors from the 
MSR Challenge data set~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy the commit's
complexity, such as the size of the changes being performed.  The technical
factors used are listed below:
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn: lines of code changed by this commit.
\item Files added: files added by this commit.
\item Files modified: files modified by this commit.
\item Tests added: tests added by this commit.
\item Tests deleted: tests deleted by this commit.
\item Source files: files in project at the time of the commit.
\item Source loc: lines of source code in the project at
	the time of the commit.
\item Travis status: status of the Travis build integration.
\end{itemize}

\textbf{Social Factors:} To collect the social data, we created a web scraper to extract the social data
from developer's profiles.
We used the commit hash and the project name in the original data
set provided by the MSR Challenge~\cite{msr17challenge} to locate the web page
of the commit, leveraging \textit{github.com}'s URL standard for projects and
commit hashes.
%  using the syntax
% below. 
% \newline \newline
% \textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
% \newline \newline

@@

\begin{itemize}
\item Repositories: the repositories the developer has access to. This 
includes repositories the developer owns, repositories the developer contributes
to, and repositories for which the developer has organizational membership access.
\footnote{https://developer.github.com/v3/repos/}
\item Stars: a count of the projects the developer has stared. Starring a project
to shows approval of the repository and creates  a bookmark for later 
access.\footnote{https://help.github.com/articles/about-stars/}
\item Followers: number of developers that follow the author. 
\item Following: number of developers that the author follows 
\item Contributions in the last year: number of contributions made by the author in the last year.
\end{itemize}

@@

\textbf{Comparing two data sets:} We used the social data gathered to create two data 
sets: one with only the technical
factors and the build status, and another with both the technical and social
factors. We performed this split to analyze how well technical factors alone,
and then both technical and social
factors predict build integration status.

The data set used in this study~\cite{msr17challenge} is very diverse.
and consists of commits from multiple years ago. The social data we 
gather is recent, gathered in January 2017. In an effort to mitigate the threat of
using future result to predict previous events,
we removed the commits in the data set that were not performed within the last
three years of the data set's release (2014,2015,2016).  While this is not
a perfect solution , we believe that these numbers are unlikely to have changed
significantly in the last three years.

@@

The high ratio of successful to not successful builds cause the classifier to 
favor misclassifying not successful builds over successful builds, because a 1\%
misclassification rate in 3/4th of the data is greater than a 1\%
misclassification rate in 1/4th of the data.  To penalize misclassification for
both classes equally, we created a separate data set where the
successful builds equaled the number of not successful builds.  
We build this data set by copying over all not successful builds and randomly
selecting a sub-sample of the successful builds until the two build status were
equal, a process known as downsampling.  We used 
both the downsampled and non-downsampled data sets in our results to show the 
difference of the behavior of the decision tree when it is trained with a equal 
ratio than when it is trained with a unequal ratio.

@@

@@

Table~\ref{resultsTable} shows the results of running the two data sets through the
default Weka J48 decision tree algorithm, first without downsampling. The 
decision tree shows an increase of 4.09\% correctly classified instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
had a classification accuracy of 64.10\%, which outperformed the baseline of
guessing all builds passed (50.00\%).
 After including the social data
in the data set, the classifier correctly predicted 76.09\% of the data set,
about a 12\% improvement from only the technical data.  These results show that
both technical and social data can be used to improve predictions of build 
integration success.

It is also worth noticing that in both cases the Kappa statistic increases when adding social data (100\% and 85\% respectively) which represents a more robust measure than Correctly classified instances, since it takes into account the correctly guessed instances occurring by chance, and we may also notice that the Mean absolute error decreases, giving stronger confidence to our claims when considering eventual outcomes.

@@

To determine if core team member's have greater build success rates,
we classified the build success rate for
core team members and non-core team members in the data set without 
downsampling.  We found that core team members
triggered 89.39\% of the builds in the data set and 75.58\% of those builds
passed.  Non-core team members triggered 10.61\% of the builds in the data set
and 64.70\% of the builds passed.  This shows that core team members are more
likely to have a successful build integration than non-core team members.

@@

We also investigated if developers with followers were more likely to have a
successful build integration, since have followers may be seen as vouching for
the developer's abilities.  We specifically investigated if a developer with 
followers was more likely to pass the build in the data set without 
downsampling.  We found that only 0.87\% of the
contributions in the data set was performed by developers with zero 
followers (excluding the developers in which we were not able to extract profile
information for). We found that 99.13\% of the contributions were performed by
developers with at least one or more followers.
Developers with 0 followers had a successful build commit 68.49\%
of the time.  Developers with one or more followers were successful 74.78\% of
the time.

@@

Overall, we have found that social attributes which proxy experience produce a 
noticeable increase in predicting build success.  While the increase was noticeable 
with the full data set, there was a much greater increase in prediction
accuracy after performing downsampling. These results show that social factors
as the ones studied in this paper are significant predictors when
evaluating the predictive power of build commit success.

@@

%\paragraph{External validity} 
 To tackle the concern that the results of this study might not generalize to 
 other instances outside of the studied cases, we have used a broad and rich 
 dataset~\cite{msr17challenge} in our analysis that comprises 1,359 popular projects, which help to 
 build the notion that since we are building our analysis on top of a vast 
 data set, the threat of this analysis 
 not generalizing to other projects is mitigated.

>>>>

\todo{I would like both attribute description subsections better if they
  provided a sentence (or a half sentence) of intuition explaining why the
  proposed factors might be correlated with build success.  Maybe not one
  sentence per factor (since some might be repetitive), but some epxlanation on
  the underlying intuition or theory.}

\paragraph{Technical Factors:} We collected these factors from the 
MSR Challenge data set~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy the commit's
complexity, such as the size of the changes being performed.  The technical
factors used are listed below:
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn: lines of code changed by this commit.
\item Files added: files added by this commit.
\item Files modified: files modified by this commit.
\item Tests added: tests added by this commit.
\item Tests deleted: tests deleted by this commit.
\item Source files: files in project at the time of the commit.
\item Source loc: lines of source code in the project at
	the time of the commit.
\item Travis status: status of the Travis build integration.
\end{itemize}

\paragraph{Social Factors:} To collect the social data, we created a web scraper to extract the social data
from developer's profiles.
We used the commit hash and the project name in the original data
set provided by the MSR Challenge~\cite{msr17challenge} to locate the web page
of the commit, leveraging \textit{github.com}'s URL standard for projects and
commit hashes.
%  using the syntax
% below. 
% \newline \newline
% \textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
% \newline \newline

@@

\begin{itemize}
\item Repositories: the repositories the developer has access to. This 
includes repositories the developer owns, repositories the developer contributes
to, and repositories for which the developer has organizational membership access.
\footnote{https://developer.github.com/v3/repos/}
\todo{Is this a count, or what?}
\item Stars: a count of the projects the developer has stared. Starring a project
to shows approval of the repository and creates  a bookmark for later 
access.\footnote{https://help.github.com/articles/about-stars/}
\item Followers: number of developers that follow the author. 
\item Following: number of developers that the author follows 
\item Contributions in the last year: number of contributions made by the author in the last year.
\end{itemize}

@@

\paragraph{Comparing two data sets:} We used the social data\todo{Confusing,
  since you proceed to say you build a dataset with technical factors as well as
  social factors.} gathered to create two data 
sets: one with only the technical
factors and the build status, and another with both the technical and social
factors. We performed this split to analyze how well technical factors alone,
and then both technical and social
factors predict build integration status.

The data set used in this study~\cite{msr17challenge} is very diverse.
and consists of commits from multiple\todo{How many? Please be precise.} years ago. The social data we 
gather is recent, gathered in January 2017. In an effort to mitigate the threat of
using future result to predict previous events,
we removed the commits in the data set that were not performed within the last
three years of the data set's release (2014,2015,2016).  While this is not
a perfect solution , we believe that these numbers are unlikely to have changed
significantly in the last three years.\todo{Why?}

@@

The high ratio of successful to not successful builds leads a naive classifier to 
favor misclassifying not successful\todo{everywhere you say ``not successful'',
  replace with ``unsuccessful''.} builds over successful builds, because a 1\%
misclassification rate in 3/4th of the data is greater than a 1\%
misclassification rate in 1/4th of the data.  To penalize misclassification for
both classes equally, we created a separate data set where the
successful builds equaled the number of not successful builds.  
We build this data set by copying over all not successful builds and randomly
selecting a sub-sample of the successful builds until the two build status were
equal, a process known as downsampling.  We used 
both the downsampled and non-downsampled data sets in our results to show the 
difference of the behavior of the decision tree when it is trained with a equal 
ratio than when it is trained with a unequal ratio.

@@

\todo{Maybe a quick list of the 3--4 factors you actually look at?}

@@

\todo{a better subsection heading might be ``Classification with and without
  social factors.'', since all experiments look at success classification.}
Table~\ref{resultsTable} shows the results of running the two data sets through the
default Weka J48 decision tree algorithm.  Without downsampling, the 
decision tree shows an increase of 4.09\% correctly classified instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
had a classification accuracy of 64.10\%, which outperformed the baseline of
guessing all builds passed (50.00\%).
 After including the social data
in the data set, the classifier correctly predicted 76.09\% of the data set,
about a 12\% improvement from only the technical data.  These results show that
both technical and social data can be used to improve predictions of build 
integration success.

It is also worth noticing that in both cases the Kappa statistic increases when
adding social data (100\% and 85\% respectively) which represents a more robust
measure than Correctly classified instances\todo{Whenever you use a phrase that
  is a key label in your data (like ``Correctly classified''), find a way to
  typeset it differently so it scans as an important concept.  Quotes or Italics/emphasis
  is fine.}, since it takes into account the
correctly guessed instances occurring by chance, and we may also notice that the
Mean absolute error decreases, giving stronger confidence to our claims when
considering eventual outcomes.

@@

\todo{One sentence introducing this experiment.}
To determine if core team member's have greater build success rates,
we classified the build success rate for
core team members and non-core team members in the data set without 
downsampling.  We found that core team members
triggered 89.39\% of the builds in the data set and 75.58\% of those builds
passed.  Non-core team members triggered 10.61\% of the builds in the data set
and 64.70\% of the builds passed.  This shows that core team members are more
likely to have a successful build integration than non-core team members.

@@

\todo{Maybe ``relationship with'' rather than ``effect on''?

We also investigated whether developers with followers were more likely to have a
successful build integration, since followers may be seen as vouching for
the developer's abilities.  We specifically investigated if a developer with 
followers was more likely to pass the build in the data set without 
downsampling.  We found that only 0.87\% of the
contributions in the data set was performed by developers with zero 
followers (excluding the developers in which we were not able to extract profile
information for). We found that 99.13\% of the contributions were performed by
developers with at least one or more followers.
Developers with 0 followers had a successful build commit 68.49\%
of the time.  Developers with one or more followers were successful 74.78\% of
the time.

@@

Overall, we have found that social attributes which proxy experience\todo{, such
  as, example,} produce a 
noticeable increase in predicting build success.  While the increase was noticeable 
with the full data set, there was a much greater increase in prediction
accuracy after performing downsampling. These results show that social factors
as the ones studied in this paper are significant predictors when
evaluating the predictive power of build commit success.

@@

%\paragraph{External validity} 
 To tackle the concern that the results of this study might not generalize to 
 other instances outside of the studied cases, we have used a broad and rich 
 dataset~\cite{msr17challenge} in our analysis that comprises 1,359 popular projects, which help to 
 build the notion that since we are building our analysis on top of a vast 
 data set, the threat of this analysis 
 not generalizing to other projects is mitigated.
\todo{mention the threat of the collapsing of data as you were discussing over email.}
